\Title

### 2020-02-28 manuscript/manuscript.tex
Save parameters as LaTeX variables
Instead of programmatically creating the LaTeX tables for parameters,
list of parameters values are stored as LaTeX values and then the tables
are created manually, filling each cell with these variables.
Add curly braces after LaTeX variables
Without the braces, LaTeX does not compile spaces after the variables.

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}

@@

The synthetic model is made out of \NPrisms prisms distributed on a region of
\ModelEasting$\times$\ModelNorthing between \ModelDepth deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity and \ModelMaxDensity.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize$\times$\TargetNorthingSize points with a spacing of
\TargetSpacing located \TargetHeight above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize$\times$\TargetNorthingSize points with
        a spacing of \TargetSpacing located \TargetHeight above the zero height
        plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting$\times$\SurveyNorthing.
The ground survey is composed by \GroundSurveyPoints observation points distributed at heights
ranging between \GroundSurveyMinHeight and \GroundSurveyMaxHeight
(Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints points at heights between
\AirborneSurveyMinHeight and \AirborneSurveyMaxHeight.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-ground-survey}
    \input{parameters_ground_survey.tex}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-airborne-survey}
    \input{parameters_airborne_survey.tex}
\end{table*}

>>>>

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}

@@

The synthetic model is made out of \NPrisms{} prisms distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity{} and
\ModelMaxDensity{}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
        zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
The ground survey is composed by \GroundSurveyPoints{} observation points
distributed at heights ranging between \GroundSurveyMinHeight{} and
\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints{} points at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \GroundSourceBellowDataConstantDepthDepth
              & \GroundBlockMedianSourcesConstantDepthDepth
              & \GroundGridSourcesConstantDepthDepth \\
        Spacing & -
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataRelativeDepthDepth
              & \GroundBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataVariableDepthDepth
              & \GroundBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \AirborneSourceBellowDataConstantDepthDepth
              & \AirborneBlockMedianSourcesConstantDepthDepth
              & \AirborneGridSourcesConstantDepthDepth \\
        Spacing & -
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataRelativeDepthDepth
              & \AirborneBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataVariableDepthDepth
              & \AirborneBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}
